\section{Peaceful Coexistence of Special Relativity and Quantum Physics}
So far we've seen that PI holds in the Copenhagen interpretation (section \ref{PISec}), that OI holds in the Bohmian interpretation (section \ref{OISec}), and that due to the violation of Bell's inequality, it is not possible for both OI and PI to hold in a model that is consistent with physical reality (section \ref{OISec}). Nevertheless, as long as PI holds, the failure of OI does not enable Bob to send messages to Alice faster than light because Bob only has control over the measurement choice he makes rather than the outcome he observes. Assuming Bob's mental states have no effect on the measurement outcome, there is nothing he can do to influence his outcome, so although Alice will be able to work out or at least get some information about Bob's measurement outcome if she already happens to know which choice of measurement he has made, she will not be able to work out which measurement Bob makes (or even whether Bob has made a measurement at all) by measuring the outcome of her particle. For Shimony,\footnote{See \cite[146-147]{Shimony86}.} this inability to send superluminal messages between Alice and Bob when PI holds and OI is violated was deemed sufficient for  standard quantum theory and special relativity to peacefully coexist. 

However, Butterfield is not satisfied with Shimony's solution to peaceful coexistence.\footnote{See \cite[p. 12]{Butterfield}.} Firstly, he notes that proofs of non-superluminal signaling\footnote{e.g. see \cite[p. 113--116]{Redhead}; \cite[p. 139--140]{Hiley}} make no assumptions about spacetime locations.\footnote{For a definition of a spacetime location, see page \pageref{spacetimedef}.} One would have thought that any proof that superluminal signalling between two points is impossible would have to show that a signal cannot be transmitted from one point to the other in less time than the time it takes light to travel between the two points. But if nothing is said about the location of these two points or what is so special about the speed of light compared to the speed of any other particle, then there does not seem to be enough information in the premises to draw the desired conclusion that superluminal signaling is impossible in quantum physics.

Secondly,  Butterfield notes that Shimony thinks peaceful coexistence of quantum physics and special relativity is guaranteed by the denial of OI and the acceptance of PI. However, OI itself depends on the (often) rather vague notion of what an outcome really is. For instance, in the many-worlds interpretation, it is not clear that there are any outcomes at all. Rather, there is just a universal quantum state that tells us the probability of certain outcomes, if there were such things as outcomes -- it doesn't tell us that there really are any outcomes. In the next chapter, we will discuss the many-worlds interpretation and why denying the reality of outcomes is such an unsatisfactory way of guarantying peaceful coexistence of quantum physics and special relativity. But as is clear from other interpretations of quantum physics, the notion of what an outcome is doesn't have to be vague. In the Bohmian interpretation of quantum physics, it is very clear what an outcome of an experiment is since all the particles have definite positions and momenta. Because of this, the pointers and displays of measuring devices which are made up of particles will have definite readouts which will correspond to the definite positions of particles being measured (assuming the measurement device is working properly). So unlike the many-worlds interpretation, measurements in the Bohmian interpretation have definite outcomes, and hence there is only a single world in the Bohmian interpretation of quantum physics. But as we've just seen, the problem with the Bohmian interpretation is the violation of PI.

Thus, a satisfactory account of the peaceful coexistence of quantum physics and special relativity requires an interpretation of quantum physics in which not only PI holds, but also an interpretation of quantum physics that has special relativity built into it (thus satisfying Butterfield's first objection), and in which we can make sense of what it means to be an outcome (thus satisfying Butterfield's second objection).\footnote{If PI holds, then OI can't hold in a theory that makes the same predictions as standard quantum theory. But one might still worry that  a violation of OI will require some sort of superluminal causation. After all, if there is a correlation between results, there needs to be some sort of explanation of the correlation. Putting it anthropomorphically, how is Bob's system to know that Alice's system collapsed, or vice versa if there is no superluminal causality? One response to this worry is to suggest that maybe there is no collapse in the correct theory. There can still be outcomes in theories that don't have collapses, just as in the Bohmian interpretation. Furthermore, one might suppose that there could be some cause which atemporally determines Alice and Bob's measurements to have different outcomes. For example, one could imagine a supernatural being surveying a four dimensional spacetime landscape, and that this being had the power to make different events correlate with each other. So for instance, if the supernatural being saw that Alice and Bob were going to measure the spin of their respective particles along the same axis, the supernatural being could make it so that Alice got spin up and Bob got spin down with respect to the axis of measurement. Although physicists may find this scenario rather far-fetched, it doesn't entail that there is any superluminal causation by which Alice's particle affects Bob's particle or vice versa.} 

To fully address Butterfield's first objection would require quantum field theory, and this would be beyond the scope of this dissertation. But a more modest aspiration that would go some way to address Butterfield's first objection would be to insist on an interpretation of quantum physics which has a clear notion of outcome and which also has a property known as Lorentz invariance. This provides a motivation for the consideration of Kent's theory of quantum physics that has this property of Lorentz invariance. But before we consider Kent's theory, in the next chapter we will examine the many-worlds interpretation of quantum physics discussing both its appeal and its drawbacks.
